%
% $Id: ref.tex,v 1.3 2003/06/16 11:57:20 j_novak Exp $
%
\begin{thebibliography}{123}

\bibitem{York79}
J.W.~York : {\em Kinematics and dynamics of general relativity},
in {\em Sources of Gravitational Radiation}, Ed.
L.L.~Smarr, Cambridge University Press, Cambridge (1979), p.~83.

\bibitem{MisneTW73}
C.W.~Misner, K.S.~Thorne \& J.A.~Wheeler : {\em Gravitation},
Freeman, New York (1973).

\bibitem{GourgB93}
E. Gourgoulhon \& S. Bonazzola : {\em Noncircular axisymmetric stationary
spacetimes},
Phys. Rev. D {\bf 48}, 2635 (1993).

\bibitem{York72}
J.W. York : {\em Role of conformal three-geometry in the dynamics of
gravitation},
Phys. Rev. Lett. {\bf 28}, 1082 (1972).

\bibitem{ShibaN95}
M. Shibata \& T. Nakamura : {\em Evolution of three-dimensional gravitational 
waves: Harmonic slicing case},
Phys. Rev. D {\bf 52}, 5428 (1995).

\bibitem{BaumgS98}
T.W.~Baumgarte \& S.L.~Shapiro : {\em Numerical integration of
Einstein's field equations},
Phys. Rev. D {\bf 59}, 024007 (1998).

\bibitem{York99}
J.W.~York : {\em Conformal ``thin-sandwich'' data for the initial-value
problem of general relativity},
Phys. Rev. Lett. {\bf 82}, 1350 (1999).

\bibitem{AlcubABSS00}
M. Alcubierre, G. Allen, B. Br\"ugmann E. Seidel \&  W.-M. Suen : 
{\em Towards an understanding of the stability properties of the 3+1 
evolution equations in general relativity},
Phys. Rev. D {\bf 62}, 124011 (2000).

\bibitem{AlcubBMS99}
M. Alcubierre, B. Br\"ugmann, M. Miller \& W.-M. Suen : {\em Conformal 
hyperbolic formulation of the Einstein equations},
Phys. Rev. D {\bf 60}, 064017 (1999).

\bibitem{Dirac59}
P.A.M. Dirac : {\em Fixation of coordinates in the Hamiltonian theory
of gravitation},
Phys. Rev. {\bf 114}, 924 (1959).

\bibitem{Deser03}
S. Deser : {\em Some remarks on Dirac's contributions to general 
relativity},
lecture at {\em Dirac Centennial Symposium, Florida State University, 
December 2002}, preprint gr-qc/0301097.

\bibitem{AlcubB01}
M. Alcubierre \& B. Br\"ugmann : {\em Simple excision of a black hole 
in 3 + 1 numerical relativity},
Phys. Rev. D {\bf 63}, 104006 (2001).

\bibitem{HawkiE73}
S.W.~Hawking \& G.F.R. Ellis : {\em The large scale structure of 
space-time}, 
Cambridge University Press, Cambridge (1973). 

\bibitem{Wald84}
R.M.¬Wald : {\em General relativity}, 
University of Chicago Press, Chicago (1984). 

\bibitem{Thorn80}
K.S.~Thorne  : {\em Mulitpole expansions of gravitational radiation} ,
Rev. Mod. Phys. {\bf 52}, 299 (1980).

\bibitem{Mathe62} 
J.~Matthews : {\em Gravitational multipole radiation}, 
J. Soc. Ind. Appl. Math. {\bf 10}, 768 (1962).

\bibitem{Zeril70} 
F.J.~Zerilli : {\em Tensor harmonics in canonical form for
gravitational radiation and other applications},
J. Math. Phys. {\bf 11}, 2203 (1970).

\bibitem{ReggeW57}
T.~Regge \& J.A.~Wheeler : {\em Stability of a Schwarzschild singularity}, 
Phys. Rev. {\bf 108}, 1063 (1957).

\end{thebibliography}

